### 2024-03-27 doc/sections/mav-extensions.tex
[ tex ] future work notes

\section{Extensions}\label{sec:mav-extensions}

\subsection{Additive Units}

\subsection{Multiplicative-Additive Linear Logic}

\subsection{Display Calculus}

@@

>>>>

\section{Conclusions and Future Work}\label{sec:mav-extensions}

\bob{Summarise what we've done here}

\bob{This is all just notes for now}

\subsection{Future Work: Extensions to MAV}

\subsubsection{Additive Units}

I think this will be easy.

\subsubsection{Probabilistic Additives}

Ross's CSL paper.

\subsubsection{Exponentials, Kleene Star, and Inductive Propositions}

Adding $\oc P$ and $\wn P$, as in System NEL. Adding a Kleene Star as
exponential for $\vSeq$, which could bring us close to Concurrent
Kleene Algebra (Hoare et al.).

Baelde's fixpoint logic.

\subsection{Future work: Other Substructural Logics}

\subsubsection{Multiplicative-Additive Linear Logic}

Can probably recreate Okada's result using $+$-closed

\subsubsection{Bunched Implications}

I'm pretty sure that the sheaf construction here can be used to do
bunched implications too, reproducing Frumin's result in a different
way.

\subsubsection{Display Calculus}

@@

\subsection{Future Work: Proof Semantics and Categorical Coherence}

We have done provability semantics of MAV.
